---
title: "Shiny Application and Reproducible Pitch"
author: "Han Zhang"
date: "September 8, 2017"
output: ioslides_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## Instructions

This peer assessed assignment has two parts. 

First, you will create a Shiny application and deploy it on Rstudio's servers. 

Second, you will use Slidify or Rstudio Presenter to prepare a reproducible pitch presentation about your application.



## About BMI Calculation

```{r, echo = TRUE}
Height = 1.8 #unit: m
Weight = 70 #unit: kg

BMI <- Weight/(Height * Height)

BMI
```

```{r, echo = TRUE}
Height = 70 #unit: inch
Weight = 154 #unit: lb

BMI <- Weight/(Height * Height) * 703

BMI
```

## Shiny Application

radioButtons: select input unit (kg & m / lb & in)

numericInput: Value of Weight

numericInput: Value of Height

BMI value is calculated on server side

Display the calculated BMI 

Display Diagnostic



## Project Links

The shiny application developed for this assignment is available at: https://xiaohan98.shinyapps.io/Shiny_Application_and_Reproducible_Pitch/

The source codes of ui.R and server.R available on GitHub repo at: https://github.com/xiaohan98/Shiny_Application

